Specialisation \& the Latitude-niche-breadth Hypothesis

### 2015-10-12 talk/ABC_2015.tex
A few small touches
Ok, just need discussion
we need to fix the ratio on the summer plot

% %%Start Introduction Slides%%
\section*{Background}

@@

@@

    \vspace{.3cm}
    \end{center}
      \hspace{.74cm}
      {\Large      
      $G \approx aS^{\color{purple}b}$}
  \end{frame}

@@

  \begin{frame}{Lake \& Stream Food Webs}
    \begin{center}
      \includegraphics*[width=.9\textwidth]{Figures/results/effect_mod.eps}

      \vspace{1cm}
      {\color{white} Scaling increases with latitude\\
      Narrower niches in the tropics\\
      \vspace{.54cm}      
      Supports Vazquez \& Stevens 2004\\}
      {\color{white} narrower niches in the tropics}

@@

  \begin{frame}{Lake \& Stream Food Webs}
    \begin{center}
      \includegraphics*[width=.9\textwidth]{Figures/results/effect_mod.eps}

@@

  \begin{frame}{What's different in freshwaters?}
    Seasonality?\\
    NZ streams are weird but probably don't affect much\\
    Gape limitation?\\
  \end{frame}

>>>>

\section*{Background}

@@

      {\color{white}23 October 2015 | ABC 2015}

@@

    \vspace{.3cm}
      {\Large      
      $G \approx aS^b$}
    \end{center}
  \end{frame}

    \begin{center}

      Want to show a dummy negative Gen vs. Lat due to S

@@

  \begin{frame}{Lake \& Stream Food Webs}
    \begin{center}
      \includegraphics*[width=.75\textwidth]{Figures/results/effect.eps}

      \vspace{1cm}
      {\color{white} Scaling increases with latitude\\
      Narrower niches in the tropics\\
      \vspace{.54cm}      
      Supports Vazquez \& Stevens 2004\\}
      {\color{white} Narrower niches in the tropics}

@@

  \begin{frame}{Lake \& Stream Food Webs}
    \begin{center}
      \includegraphics*[width=.75\textwidth]{Figures/results/effect.eps}

@@

\section*{Freshwaters}

  \begin{frame}{What's different in freshwaters?}
    \begin{block}{They're highly seasonal}

      \begin{columns}
        \column{.5in}
        \column{2in}

        \begin{center}

        \includegraphics[width=.8\columnwidth]{Figures/spring_stream.eps}

        \includegraphics[width=.8\columnwidth]{Figures/fall_stream.eps}

        \column{2in}

        \begin{center}

        \includegraphics[width=.8\columnwidth]{Figures/summer_stream.eps}

        \includegraphics[width=.8\columnwidth]{Figures/winter_stream.eps}

        \column{.5in}

      \end{columns}
    \end{block}
  \end{frame}

  \begin{frame}{What's different in freshwaters?}
    \begin{block}{They're highly seasonal - except in NZ}
      [same pics]
    \end{block}
  \end{frame}

  % Heading off the "but so are terrestrial" issue
  \begin{frame}{What's different in freshwaters?}
    \begin{block}{They're aquatic}

      [picture of a fish vs. a land beast]
      [gape limitation]

    \end{block}
  \end{frame}

\section*{Conclusion and Acknowledgements}
  \begin{frame}{So why are there more species in the tropics?}
    \begin{block}{Estuarine, marine, \& terrestrial}
      \begin{itemize}
        \item Broader niche space in the tropics
        \item Similar specialisation everywhere
      \end{itemize}
    \end{block}

    \begin{block}{Lakes \& Streams}
      \begin{itemize}
        \item Narrower niches in the tropics
        \item Generality due to seasonality?
      \end{itemize}
    \end{block}
  \end{frame}

  \begin{frame}{Acknowledgements}
    \begin{columns}
      \column{.25in}

      \column{1.5in}
      \centering

      Daniel B. Stouffer\\
      \& his lab

      \column{1.5in}
      \centering

      Tamara N. Romanuk\\
      \& her lab

      \column{1.5in}
      \centering

      Angus McIntosh\\
      Matthias Schleuning

      \column{.25in}
    \end{columns}
    \begin{columns}
     \column{2.5in}
       \centering

      \vspace{.25cm}

       \includegraphics[width=0.6\columnwidth]{marsden-logo-cmyk-tif.eps}

      \vspace{.25cm}

      \includegraphics[width=0.7\columnwidth]{Dal_logo.eps}

     \column{2.5in}
       \centering

      \vspace{.25cm}

       \includegraphics[width=0.7\columnwidth]{NSERC_C.eps}

       \vspace{.25cm}

       \includegraphics[width=0.4\columnwidth]{logo-canterbury-color.eps}

       \vspace{.5in}

    \end{columns}
  \end{frame}

  \begin{frame}{Latitude affects scaling - sometimes}

  [Show the 5-panel plot, the equation.]
